Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Wording + grammar

Hspec provides an EDSL for defining specs.  A spec organizes evidence
in a tree structure (or a forest, to be accurate), and is defined
with \texttt{it} and \texttt{describe}.

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence (a code example or a property) into a spec.
Code examples can be arbitrary HUnit test cases\footnote{%
Wrapping the test case with HUnit's {\tt TestCase} constructor is not
necessary.}.  Properties must be of type {\tt
Property}.  QuickCheck's \texttt{property} function can be used to turn
an arbitrary properties into values of type \texttt{Property}.

>>>>

Hspec provides an EDSL for defining specs.  A \emph{spec} organizes evidence
in a tree structure (or a forest, to be accurate), and is defined
with \texttt{it} and \texttt{describe}.

Here is an example that specifies some behavior of the {\tt reverse}
function.

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence (a code example or a property) into a spec.
Code examples can be arbitrary HUnit test cases\footnote{%
Wrapping the test case with HUnit's {\tt TestCase} constructor is not
necessary.}.  Properties must be of type {\tt
Property}.  QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into values of type \texttt{Property}.
